### 2021-09-15 about/vita.tex
Small changes here and there
Updated research page
Added various things

\newcount\submittedcount
\submittedcount=1
\def\subitem{\pubitem S\the\submittedcount. \global\advance\submittedcount by 1}
\newcount\reportcount
\reportcount=1
\def\repitem{\pubitem R\the\reportcount. \global\advance\reportcount by 1}

@@

@@

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}, 20~pp.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}, 11~pp.
Submitted December 2020.
\subitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
Submitted May 2021.
\subitem (with Jad Hamdan) The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 8~pp.
Submitted June 2021.
\subitem (with Luc Devroye and Rosie Y. Zhao) The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
Submitted June 2021.

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)
[S1, S3, S5]

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry. [R3]
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of the interactive proof assistant Harpoon and wrote OCaml code as part of
ongoing work on the functional programming language Beluga. [R2]
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing. [R1]

@@

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, A339942, and A341822
to the On-line Encyclopedia of Integer Sequences.
\medbreak

>>>>

\newcount\papercount
\papercount=1
\def\papitem{\pubitem P\the\papercount. \global\advance\papercount by 1}
\newcount\submittedcount
\submittedcount=1
\def\subitem{\pubitem S\the\submittedcount. \global\advance\submittedcount by 1}
\newcount\reportcount
\reportcount=1
\def\repitem{\pubitem R\the\reportcount. \global\advance\reportcount by 1}

@@

\sectheader{Papers}

\pubbegin P
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}, 11~pp.
To appear in {\sl Integers: Electronic Journal of Combinatorial Number Theory}, 2021.

@@

\begingroup\parindent=10pt
\thing (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}, 20~pp.
\thing (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 8~pp.
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\endgroup

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of the interactive proof assistant Harpoon and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

\leftright{\bf Bytecode compiler and interpreter}{\bf February -- June 2019}
\leftright{\sl Individual software project}{\sl Charles University}
\smallskip
Semester-long individual software project under the supervision of Adam Dingle.
Created OPythn, a bytecode compiler and virtual machine for a subset of Python.
OPythn includes support for lists, dictionaries, named and anonymous functions, objects, and classes.
It is implemented in OCaml using Ocamllex for lexing and Menhir for parsing.

@@

\leftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Hold office hours twice a week and responsible for grading of assignments.
\medbreak

@@

\parindent=10pt
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, A339942, A341822, and A347580
to the On-line Encyclopedia of Integer Sequences.
\medbreak
